\ \\ \LARGE\bf Rolling Horizon methods for Games with Continuous States and Actions

### 2014-04-01 lpaper/lunarcont.tex
Closer then ever

\newcommand{\twopartdef}[4]
{
	\left\{
		\begin{array}{ll}
			#1 & \mbox{if } #2 \\
			#3 & \mbox{if } #4
		\end{array}
	\right.
}

@@

% Paper title: keep the \ \\ \LARGE\bf in it to leave enough margin.
\title{\ \\ \LARGE\bf Rolling Horizon methods for Games with Continuous Actions } 
% TODO - better title

@@

\begin{abstract}
It is often the case that games have continuous dynamics and allow for continuous actions. For larger games with complicated dynamics, having agents learn offline behaviours is a daunting task. On the other hand, provided a forward model is available, one might try to spread the cost of search in a rolling horizon fashion (e.g. as in example MCTS). In this paper we compare HOLOP, an open loop planning algorithm and a version evolutionary planning using CMA-ES. He show that rolling horizon CMA-ES outperforms HOLOP in two classic benchmark problems (Cart Balancing and <problem name> ) and Lunar Lander, a classic arcade game. We conclude that off-the-shelf evolutionary algorithms can be used successfully in a rolling horizon setting.

@@

Recently, algorithms stemming from, or at least partially inspired by, MCTS aiming at solving planning problems involving continuous states and actions have come to light. A typical such algorithm is Hierarchical Optimistic Open Loop Planing (HOLOP)~\cite{weinstein2012bandit}. HOLOP is based partially on a strong~\cite{hoo2011} real-valued optimisation algorithm called HOO (for ``Hierarchical Optimistic Optimisation''). In this paper two major contributions are made plus a smaller ``add-on''; the first contribution is the comparison of two versions of a very popular and strong evolutionary strategy: Covariance Matrix Adaptation Evolutionary Strategy (CMA-ES)~\cite{hansen2003reducing} and its Uncertainty Handling version UH-CMA-ES~\cite{hansen2009tec} with Truncated Hierarchical Optimistic Optimisation (T-HOO)~\cite{hoo2011} on the
Black Box Optimisation Problem (BBOP) benchmark suit~\cite{bbopnoisy}.  T-HOO is a faster version of HOO~\cite{hoo2011}, an algorithm reminiscent of Monte Carlo Tree Search. The experiments are conducted using similar conditions to those an agent would face if it was to solve planning problems. Our second contribution is to incorporate CMA-ES and UH-CMA-ES into three versions of an algorithm called EOLOP, for Evolutionary Open Loop Optimistic Planning.  This algorithm uses evolution instead of tree search for implementing sample-based control algorithms. We then proceed to test the algorithms proposed on noisy versions of standard reinforcement learning (RL)
benchmarks, namely the inverted pendulum and the double integrator problems. Our ``extra'' contribution is an add-on for evolutionary algorithms (transfered from HOLOP) that can help when the number of function evaluations is very small.

While evolution is commonly used to evolve a reactive neural network controller (in a process commonly called neuro-evolution) for these and other RL problems,
it should be noted that evolution is being applied in a very different way here. In this paper, evolution is applied to perform each action given the current state.  This approach can only be applied when a generative
model is available, but has the advantage of offering immediate good performance without any
prior learning.  The disadvantage, compared to neuro-evolution, is that every action performed requires
CPU time for the simulations.  This is described in more detail in section \ref{Planning}.

The rest of this paper is structured as follows.  Section \ref{Optimisation} discusses the relevant base algorithms that are going to be used in this paper, ((Truncated) Hierarchical Online Optimisation~\cite{hoo2011} and CMA-ES~\cite{hansen2003reducing}).
Section~\ref{Planning} explains why and how the above algorithms can be used in the context of planning. Section \ref{evo} describes how one can incorporate evolution into this, making this our main contribution section from an algorithmic standpoint. In Section \ref{Methodology} the experimental setup is described. In Section~\ref{sec:Experiments} a number of experiments are portrayed and analysed.  These form the bulk of this paper's contribution. We conclude with a short discussion in Section \ref{Conclusion}.

% TODO - actually determine what the core essence of what it is we're doing here before writing the introduction

\section{Motivation}

\subsection{Solving Continuous Problems with Continuous Actions} % this title is awful and it needs changing

Previous research into using MCTS to provide solutions for continuous physics-based problems have examined cases such as the Physical Travelling Salesman Problem \cite{perez14}. Within these continuous contexts, discrete actions have proven to be quite effective, especially with use of macro-actions and some degree of higher level planning \cite{powley12}.  % this section seems clunky

{\itshape Lunar Lander} is an excellent test case to study for many reasons, due to its inherently multi-objective nature. With the objectives to both land quickly while also minimising velocity changes, which cost fuel which must be conserved, it has been an interesting scenario to examine the properties and constraints imposed just by the environment alone. While there have been attempts to solve this deceptively complex problem before using discrete macro-actions \cite{roberts13}, in this paper the problem is being approached as one that can be better solved with continuous actions.

\section{Planning}  \label{Planning}
In this section a formalised version of planing will be presented and an explanation provided on how the algorithms described in the previous section can be used to attack the problem.
\subsection{Markov Decision Processes}

@@

\begin{itemize}
\item $S$ is a set of states, $s \in S$, where $s_j^t$ is state $j$ at time $t$ and $s'_j$ is the state j at time $t+1$.
\item $A$ is a set of actions, each action named $a_j$.
\item  $T:S \times \S \times  A  \rightarrow [0,1]$ is the probability of moving from state $s$ to state $s'$  after action $a \in A$ has taken place. $T(s'|s,a)$ denotes this probability.
\item  $R:S \rightarrow \Re$, $R(s)$ is a reward function at each state.
\item $\gamma$, a discount factor.
\end{itemize}

The MDP defines a single agent environment, fully observable to the agent. In an MDP, the Markov property holds (hence the name), which means that all the information an agent needs in order to act is embedded in the current state.
A possible route of action an agent might take is known as the \textit{policy} $\pi$. A policy is a probabilistic mapping between state and actions, $\pi:S \times A \rightarrow [0,1]$, thus $\pi(s,a) \in [0,1]$,  $\sum_{a\in A}{\pi(s,a)} = 1$. The set of all policies is denoted as $\Pi$. The goal of an agent in an MDP environment is to maximise its long term value $V(\pi,s_0) = R(s) + \sum\limits_{s\in S}\sum\limits_{a\in A} \gamma \pi(s,a)T(s^\prime|s,a)  V(\pi,s^\prime) $, by assigning the probability of actions to take at each state.

@@

Since an open loop policy is now a real-valued vector of actions, algorithms like T-HOO and CMA-ES can be used to find such a policy. Hence the title of this paper:  Rolling Horizon Open-loop Policy Evolutionary Learning. To the best of our knowledge this is the first time evolution has been used in such a setting. There are examples of closed loop rolling horizon papers, but these are beyond the scope of this article~\cite{xiang2012differential,samothrakis2010planning}.

\subsection{Planning using a Generative Model}

@@

Once a satisfactory plan/policy has been estimated (or the agent runs out of time, iterations etc. ) it proceeds by executing the first action of the plan, thus moving to the next state. Once there, the agent performs the same sequence of ``mental'' actions, (i.e. plans and executes the first action), until some predefined stopping condition.  In this paper we will concern ourselves \textit{only} with this method of planning. What changes from method to method is how the plan is formed.

In standard UCT, a procedure similar to temporal difference learning is followed, where one learns the value of each state. An agent then forms a policy by choosing a value greedily. In our case, because our state space has continuous states and actions, this is impossible without the use of a function approximator (or an infinite discretization of space), which is not attempted here. What is attempted though is to learn the policy function directly without reference to state, while planning continuously from the current state. So while the agent forms open-loop plans at each clock tick, in reality it is executing a closed-loop policy. While the strategy is not provably optimal, it can work well in practice~\cite{weinstein2012bandit}. This will be seen by our experimental results (see Section \ref{sec:Experiments}).

@@

\State 	\textbf{define external function} $\mathsc{FindOpenLoopPlan} (depth) $ \Comment{Try to find the optimal policy. You can use either evolution or HOO here}

	\Procedure{$\mathsc{OOOP}$} {}
		\While{$\mathit{True}$}
		    \State $a \gets \mathsc{FindOpenLoopPlan}(depth)[0]$ \Comment{Execute first action of the policy}
		    \State $s \sim T(s'|s,a)$ \Comment{Stop only at an absorbing state}
		\EndWhile
		\State
	\EndProcedure

@@

\section{Methodology}

@@

\subsection{Environment and Physics}

% this is a heavily cut down rewritten version of the physics described in sam's 2013 cig paper
% more detail will be added depending on if it is appropriate or not

@@

\subsection{Continuous Action MCTS} % this can be renamed something much better presumably

% TODO - meeting or discussion might be good to be entirely certain on what's going on in the code
% DISCUSS IN MEETING: use of a two-stage approach: might be good to mention this?? temporary holdover?????

\section{Results}

@@

  \centering
        \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{graphics/online-IP-crop.pdf}
                \caption{Scores for a noise level of $l=1$ under variable function evaluations.\vspace{0.14in} }
                \label{fig:IP}
        \end{subfigure}   \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{graphics/online-noise-IP_50-crop.pdf}
                \caption{Scores for 50 iterations under variable noise level $l$. Notice how UH-EOLOP fails to balance the pole.}
                \label{fig:IP-N-50}
        \end{subfigure}  \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{graphics/online-noise-IP_100-crop.pdf}
                \caption{Score for 100 iterations under variable noise level $l$.\vspace{0.14in}}
                \label{fig:IP-N-100}
        \end{subfigure}%

@@

\section{Conclusion}

% pending
% DISCUSS IN MEETING: this entire section

% Use \section* for the acknowledgments
\section*{Acknowledgements}
Samuel Roberts is supported by an EPSRC PhD Studentship.
% any other acknowledgements??

>>>>

\newcommand{\twopartdef}[4]
{
	\left\{
		\begin{array}{ll}
			#1 & \mbox{if } #2 \\
			#3 & \mbox{otherwise } 
		\end{array}
	\right.
}

@@

% Paper title: keep the \ \\ \LARGE\bf in it to leave enough margin.
\title{\ \\ \LARGE\bf Rolling Horizon methods for Games with Continuous States and Actions } 
% TODO - better title

@@

\begin{abstract}
It is often the case that games have continuous dynamics and allow for continuous actions, possibly with with some added noise. For larger games with complicated dynamics, having agents learn offline behaviours in such a setting is a daunting task. On the other hand, provided a forward model is available, one might try to spread the cost of search/learning in a rolling horizon fashion (e.g. as in Monte Carlo Tree Search). In this paper we compare T-HOLOP (Truncated Hierarchical Open Loop Planning), an open loop planning algorithm at least partially inspired by MCTS with a version evolutionary planning using CMA-ES (which we call EVO-P) in two planning benchmark problems (Cart Balancing and the Double Integrator) and Lunar Lander, a classic arcade game. He show that EVO-P outperforms T-HOLOP in almost all settings. We conclude that off-the-shelf evolutionary algorithms can be used successfully in a rolling horizon setting, and might offer considerable advantages over more formal methods.

@@

Recently, algorithms stemming from, or at least partially inspired by, MCTS aiming at solving planning problems involving continuous states and actions have come to light. A typical such algorithm is Hierarchical Optimistic Open Loop Planing (HOLOP)~\cite{weinstein2012bandit}. HOLOP is based partially on a strong~\cite{hoo2011} real-valued optimisation algorithm called HOO (for ``Hierarchical Optimistic Optimisation''). In this paper two contributions are made; the first contribution is the comparison of two versions of a very popular and strong evolutionary strategy: EVO-P, the open loop planning algorithm using Covariance Matrix Adaptation Evolutionary Strategy (CMA-ES)~\cite{hansen2003reducing} with a version of HOLOP, which stands for Hierarchical Open Loop Optimistic Planning~\cite{hoo2011} on two standard benchmark problems, the double integrator and the reverse pendulum.  For speed purposed, we use T-HOO (Truncated Hierarchical Optimistic Optimisation), a faster version of HOO~\cite{hoo2011}, as the engine of HOLOP, hence we name the algorithm used T-HOLOP.  Our second contribution is the use of the these algorithms in Lunar Lander, a popular arcade game, coupled with a strong two-stage heuristic. We show that while EVO-P performs really well, T-HOLOP struggles.

While evolution is commonly used to evolve a reactive neural network controller (in a process commonly called neuro-evolution) for these and other RL problems,
it should be noted that evolution is being applied in a very different way here. In this paper, evolution is applied to perform each action given the current state.  This approach can only be applied when a generative
model is available, but has the advantage of offering immediate good performance without any
prior learning.  The disadvantage, compared to neuro-evolution, is that every action performed requires
CPU time for the simulations.  This is described in more detail in section \ref{sec:Planning} and in line with what is being done in Perez et al. \cite{perez2013rolling}, although this time in a continuous setting.

The rest of this paper is structured as follows.  Section \ref{sec:Optimisation} discusses (briefly and epigrammatically) the relevant base algorithms that are going to be used in this paper, ((Truncated) Hierarchical Online Optimisation~\cite{hoo2011} and CMA-ES~\cite{hansen2003reducing}).
Section~\ref{sec:Planning} explains why and how the above algorithms can be used in the context of planning (and thus transformed into HOLOP and EVO-P respectively).  In Section \ref{sec:methodology} the experimental setup is described. In Section~\ref{sec:Experiments} a number of experiments are portrayed and analysed.  These form the bulk of this paper's contribution. We conclude with a short discussion in Section \ref{sec:conclusion}.

\section{Algorithms for Continuous Function Optimisation} \label{sec:Optimisation}

This is the first background section of this paper, which aims to introduce the two core optimisation algorithms on which our contributions are made. We will present both algorithms from an implementer's viewpoint, without explicitly justifying the design and mathematical choices behind them, nor going into too much detail. Interested readers should look at the cited bibliography for extensive discussions.

In general, the optimisation problem can be defined as: Given a function $f:\bm{X}\rightarrow Y $, where $X \in \mathcal{R}^n$, with $n$ being the length of vector $\bm{X}$. The domain $\bm{X}$ is usually called the search space. Our goal is to find a vector $\bm{x}_0$, for which $f(\bm{x}) > f(\bm{x_0}) $ for all $x$ (also known as ``minimisation'') or $f(\bm{x}) < f(\bm{x_0})$ for all $x$ (known as ``maximisation'').
There are an enormous number of algorithms devoted to this problem, but only two will be presented and compared here, which are both considered state of the art in their respective fields and do not require the calculation of a gradient. If one has an analytic expression of the gradient or if the functions proposed are smooth enough, it might be better to look elsewhere for solutions (e.g. Conjugate Gradient Methods~\cite{shewchuk1994introduction}).

\subsection{CMA-ES} \label{sec:algCma}

The Covariance Matrix Adaptation - Evolutionary Strategy (CMA-ES) is an evolutionary algorithm designed for continuous domains, specially suited for non-linear and non-convex optimization problems~\cite{Hansen2006}. In general, this algorithm is applied to those problems that are not constrained and are made of up to $100$ dimensions.%~\footnote{\url{http://www.lri.fr/~hansen/cmatutorial-crop-crop.pdf}}

A multivariate normal distribution (MND) is a generalization of the univariate normal distribution, which is a probability distribution that has a bell-shaped probability density function (Gaussian function). A multivariate vector $X = (x_0, x_1, \dots x_N), x_i \in \mathcal{R}$ is said to have an MND if it satisfies that any linear combination from its components, $w_0x_0 + w_1x_1 + \dots + w_Nx_N$, is normally distributed.

CMA-ES creates a population of individuals by sampling from an MND: $\mathcal{N}(m,C)$, which is uniquely defined by the distribution mean $m \in \mathcal{R}^{n}$ and its covariance matrix $C \in \mathcal{R}^{n \times n}$. The top of the density function, which corresponds to $m$, also determines the translation of the distribution. The covariance matrix $C$, positive definite and symmetric, determines the shape of the distribution and its graphical interpretation: it defines an iso-density ellipsoid $\{ x_i \in \mathcal{R} | (x - m)^T C^{-1} (x - m) = 1\}$. Through the classic evolutionary setup and by making clever use of population statistics, the algorithm proceeds from generation to generation of sampling until some convergence criteria has been reached.

\subsection{T-HOO}
%$\bm{x^{C_l}_{\mathit{min}}} = \bm{x^{C}_{\mathit{min}}} $,
Recently, a family of algorithms based on discretizing the search domain has been proposed. Only one of these algorithms is going to be discussed here, Truncated Hierarchical Optimistic Optimisation (T-HOO)~\cite{hoo2011}. The T-HOO algorithm was built from the ground up to perform optimisation of noisy functions. It is an iterative, anytime algorithm, which is run for $n_0$ iterations.  The algorithm is based on a number of components. The first one is a data structure called a node and designated $\nu$. The node includes the maximum and minimum values of our search space, vectors $\bm{x_{\mathit{max}}}$ and $\bm{x_{\mathit{min}}}$ respectively. The node also has a property called $\mathit{count}$, which initially is set to zero and a property called $\mathit{sum}$, which, again, is initially set to zero. An unvisited node (i.e. $\mathit{count}=0$) is called a leaf node.  ``Splitting'' a node is the procedure of creating two children $C(\nu) = \{C_l(\nu),C_r(\nu)\}$. Both children are initialised $\bm{x_{\mathit{max}}}$ and $\bm{x_{\mathit{min}}}$ to their parents' nodes values. When there are multiple dimensions to choose from, at  at $k$ according to some random distribution. Thus, for child $C_l(\nu)$ ,   $\bm{x^{C_l}_{\mathit{max,k}}} =\bm{x^{C}_{\mathit{min,k}}} +  \left(\bm{x^{C}_{\mathit{min,k}}} - \bm{x^{C}_{\mathit{max,k}}}\right)/2 $. For the other child,  $\bm{x^{C_r}_{\mathit{min,k}}} = \bm{x^{C}_{\mathit{min,k}}} +  \left(\bm{x^{C}_{\mathit{min,k}}} - \bm{x^{C}_{\mathit{max,k}}}\right)/2 $. In other words, the father node is split into two children nodes, choosing which dimension to split uniform randomly (or according to some other criterion). Each node also has an associated value called $B(\nu)$, which is defined recursively as:  $B(\nu) = min \{U(\nu),max \{B(C_l(\nu)),B(C_r(\nu))\}\}$. Part of this equation is the term $U(\nu)$, which is defined as in Equation \ref{eq:U}:

\begin{equation}
U(\nu) = S(\nu)/N(\nu) + \sqrt{2ln n_0/N(\nu)} + \upsilon_1 \rho^h
\label{eq:U}
\end{equation}

If a dissimilarity metric is defined between different values of $\bm{X}$ as ${\lVert \bm{x}_1 - \bm{x}_2) \rVert}^\alpha$, one can set $\upsilon_1 =\sqrt{|A|}/2)^\alpha$ and $\rho = 2^{-\alpha/|A|}$. In our experiments $a = 2$. If $N(\nu) = 0$, $B(\nu) = U(\nu) = \infty$, i.e. unvisited nodes have priority. If a node has not been visited then it is called a leaf node. If a node is a leaf node, one can ``draw'' a sample from it, by uniformly randomly sampling between $\bm{x_{\mathit{max}}}$ and $\bm{x_{\mathit{min}}}$.

The algorithm works by starting at the root node (the initial node). Since the leaf node and the root node coincide, HOOT samples from it and splits it. It can now proceed to the second iteration, where the algorithm follows a route using the maximum B-value of its children nodes, which it then samples and splits. The process repeats until the maximum number of iterations $n_0$ is over. If a certain depth is exceeded there is no point splitting nodes any more (given our iteration budget $n_0$).

\section{Planning}  \label{sec:Planning}
In this section a formalised version of planing will be presented and an explanation provided on how the algorithms described in the previous section can be used to attack the problem.
\subsection{Markov Decision Processes}

@@

\begin{itemize}
\item $S$ is a set of states, $s \in S$, where $s_j^t$ is state $j$ at time $t$ and $s'_j$ is the state j at time $t+1$.
\item $A$ is a set of actions, each action named $a_j$.
\item  $T:S \times S \times  A  \rightarrow [0,1]$ is the probability of moving from state $s$ to state $s'$  after action $a \in A$ has taken place. $T(s'|s,a)$ denotes this probability.
\item  $R:S \rightarrow \Re$, $R(s)$ is a reward function at each state.
\item $\gamma$, a discount factor.
\end{itemize}

The MDP defines a single agent environment, fully observable to the agent. In an MDP, the Markov property holds (hence the name), which means that all the information an agent needs in order to act is embedded in the current state.
A possible route of action an agent might take is known as the \textit{policy} $\pi$. A policy is a probabilistic mapping between state and actions, $\pi:S \times A \rightarrow [0,1]$, thus $\pi(s,a) \in [0,1]$,  $\sum\limits_{a\in A}{\pi(s,a)} = 1$. The set of all policies is denoted as $\Pi$. The goal of an agent in an MDP environment is to maximise its long term value. Note that since here we are dealing with continuous actions and states, sets $A$ and $S$ are metric (and infinitive). Also note that we are NOT dealing with continuous time MDPs in this paper, although there is a notion of time.

@@

Since an open loop policy is now a real-valued vector of actions, algorithms like T-HOO and CMA-ES can be used to find such a policy, hence the title of this paper. To the best of our knowledge this is the first time evolution has been used in such a setting. There are examples of closed loop rolling horizon papers, but these are beyond the scope of this article~\cite{xiang2012differential,samothrakis2010planning}.

\subsection{Notes on planning using a Generative Model}

@@

Once a satisfactory plan/policy has been estimated (or the agent runs out of time, iterations etc. ) it proceeds by executing the first action of the plan, thus moving to the next state. Once there, the agent performs the same sequence of ``mental'' actions, (i.e. plans and executes the first action), until some predefined stopping condition.  In this paper we will concern ourselves \textit{only} with this method of planning. What changes from method to method is how the plan is formed. The main version of the algorithm used can be seen in Algorithm \ref{algo:ooop}.

In standard UCT, a procedure similar to temporal difference learning is followed (or, more closely, monte carlo methods), where one learns the value of each state. An agent then forms a policy by choosing a value greedily. In our case, because our state space has continuous states and actions, this is impossible without the use of a function approximator (or an infinite discretization of space), which is not attempted here. What is attempted though is to learn the policy function directly without reference to state, while planning continuously from the current state. So while the agent forms open-loop plans at each clock tick, in reality it is executing a closed-loop policy. While the strategy is not provably optimal, it can work well in practice~\cite{weinstein2012bandit}. This will be seen by our experimental results (see Section \ref{sec:Experiments}).

@@

\State 	\textbf{define external function} $\mathsc{FindOpenLoopPlan} (depth, T',S') $ \Comment{Try to find the optimal policy. You can use either evolution or T-HOO here}

	\Procedure{$\mathsc{OOP}$} {}
		\While{$!StoppingCondition$}
		    \State $a \gets \mathsc{FindOpenLoopPlan}(depth, T',S')[0]$ \Comment{Execute first action of the policy}
		    \State $s \sim T(s'|s,a)$ \Comment{Stop only at an absorbing state}
		\EndWhile
		\State
	\EndProcedure

@@

\section{Methodology} \label{sec:methodology}
Our methodology is simple, yet efficient. We test T-HOLOP and EVO-P in two simple benchmark problems (see below for more) and Lunar Lander, a classic arcade game.

@@

\subsection{Lunar Lander}
We describe the properties of Lunar Lander.

@@

@@

  \centering
        \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{graphics/online-IP-crop.pdf}
                \caption{Scores for a noise level of $l=1$ under variable function evaluations.\vspace{0.14in} }
                \label{fig:IP}
        \end{subfigure}   \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{graphics/online-noise-IP_50-crop.pdf}
                \caption{Scores for 50 iterations under variable noise level $l$.}
                \label{fig:IP-N-50}
        \end{subfigure}  \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=1.0\textwidth]{graphics/online-noise-IP_100-crop.pdf}
                \caption{Score for 100 iterations under variable noise level $l$.\vspace{0.14in}}
                \label{fig:IP-N-100}
        \end{subfigure}%

@@

An agent can modify the ship directions by applying linear thrust $\bm{a_T}$ and the angular impulse $\bm{a_I}$. The controllers have to identify a vector of real numbers $\bm{A}$, which each element of the set $a_i \in [0,1]$. Each even element of the vector represents the linear thrust, whereas each odd element represents angular velocity. Each linear thrust vector element is transformed by applying as follows:

\begin{equation}
\bm{a_I} = 5(\bm{a_I} - 0.5)
\bm{a_T} = 300\bm{a_T} 
\end{equation}

Finally each linear thrust and angular impulse is repeated for $X$ actions, the effects of which we are going to explore below.

Lunar Lander has a setup where a player gets rewards if and only if it actually lands on the pad. This creates the problem of rollouts (whether used by EVO-P or T-HOLOP) rarely will see a reward. In order to circumvent this, as it is common in other games, we use a heuristic for each state. In order to counter this tendency, as is common in games, we used a two-stage heuristic. The first stage involves the ship trying to reach the landing pad.

\begin{multline}
rng = -\sum{arccos(vl\cdot\theta)/||vl||*||\theta||} - |\boldsymbol {v_y} - V_{y}^{max}| \\
h = \twopartdef{ -|(|\boldsymbol {v}| - C) - |\boldsymbol {s}_{x} - \boldsymbol {np}_{x}||}{||\boldsymbol {s} - \boldsymbol {np}|| < D}
{rng - |\boldsymbol {v_x}|   }{Otherwise}
\label{eq:h1}
\end{multline}

In the above Equation \ref{eq:h1} the constant C denotes the maximum magnitute of speed, which we set to $C=100$. $D = 60$ is the distance from the landing point $np$ where this heuristic takes precedence.  Intuitively, the upper part of the heuristic $h$ tries to get the ship above the landing point as fast as possible while maintaining a certain speed. The second part of the heuristic tries to minimise velocity on the $x$ axis (as the ship tries to land), maintain a minimum landing speed on the $y$ axis and get a certain angle (the summation term $rng$) as close to vector $vl = (0,-1)$, i.e. help the ship stay upright through the duration of the rollout.

\section{Results} \label{sec:Experiments}
We present the results of our experiments below.

\subsection{Benchmark Problems}

For the second set of experiments we have defined the following variables. The first two involve running the experiments with a fixed rollout depth of 50, i.e. each algorithm at each step plans for 50 steps ahead. We set the noise levels to $0.1 (\mathcal{U}(0,1)-0.5)*2 l$ uniform noise for the double integrator experiment and $10 (\mathcal{U}(0,1)-0.5)*2 l$  for the Inverted Pendulum.  The variable $l$ is the noise level which defines how noisy the environment is. Initially, we performed two experiments, with a variable number of iterations and a fixed noise level of one.

An example of how the \textit{predicted} reward looks like for a $2$-step look-ahead (instead of $50$ we use in the experiments) can be seen in Figure \ref{fig:vis}. We plotted the full state-space by pushing the internal generative model two steps forward for all possible actions by discretizing each action. Notice how the predicted reward landscape changes over time as the agent moves. The continuous replanning should aim to perform the action with the highest future reward.

The results of these experiments can be seen in graphs  \ref{fig:IP} and \ref{fig:DI}. These are close to the original experiments of Weinstein and Littman~\cite{weinstein2012bandit}, only this time we varied the number
of iterations allowed for each algorithm. The original experiment had given the algorithms 200 value iterations. With this number of iterations, for the Inverted Pendulum experiment the mean reported (using HOLOP) was $-47.45$. We got a better mean using T-HOLOP
% % \footnote{We believe there is a minor bug in the HOLOP implementation Weinstein et al use.}
\footnote{This was due to a minor difference between our implementation of HOLOP and Weinstein's.}
 of $-42.94$.

 EVO-P got as score of $-41.69$. It also  seems to have a drop in performance as we increase function evaluations, presumably because it converges to a false minima without any uncertainty handling mechanism to stop this. This kind of behaviour has been observed previously in Evolutionary Algorithms~\cite{hansen2009tec} when having noisy function.

For the double integrator experiment, we had slightly different results. The Weinstein paper reports a mean of $-2.72$ for 200 iterations. Using T-HOLOP we got a better mean of $-2.62$. A far better result of $-1.74$ is obtained by EVO-P.

Results for the variable noise levels $l$ (Figures \ref{fig:IP-N-50}, \ref{fig:IP-N-100}, \ref{fig:DI-N-50}, \ref{fig:DI-N-100}) closely mimic the performance of their constant noise counterparts. For the inverted pendulum, using just 50 iterations (Figure \ref{fig:IP-N-50}) EVO-P is able to stabilise the pendulum with . This still applies if we increase the number of function evaluations to 100 (Figure \ref{fig:DI-N-100}). On the other hand, the results start to get closer to the fixed noise level experiments if we increase the number of iterations in the Inverted Pendulum experiment to 100 (Figure \ref{fig:IP-N-50}).

\section{Conclusion} \label{sec:conclusion}

% Use \section* for the acknowledgments
\section*{Acknowledgements}
This work was supported by EPSRC grant EP/H048588/1 entitled:``UCT for Games and Beyond'' and an EPSRC Ph.D studentship.
